### 2015-03-05 slides/auburn/abc.tex
Working on slides.

\begin{frame}
\newcommand{\matrixonebottom}{6.0}
\newcommand{\matrixtwobottom}{3.0}
\newcommand{\matrixthreebottom}{0.0}
\newcommand{\matrixspace}{0.285}
% \begin{picture}(300,200)(0,0)
    % \put(0,-34){
\begin{center}
\begin{tikzpicture}[shorten >=1pt,node distance=2.2cm,on grid,auto]
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*9) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1a.pdf}}};
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*8) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1a.pdf}}};
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*7) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1a.pdf}}};
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*6) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1a.pdf}}};
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*5) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1a.pdf}}};
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*4) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1b.pdf}}};
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*3) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1b.pdf}}};
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*2) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1b.pdf}}};
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*1) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1b.pdf}}};
	\node [visible on=<1->] at (0,\matrixonebottom+\matrixspace*0) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1b.pdf}}};

	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*9) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2a.pdf}}};
	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*8) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2a.pdf}}};
	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*7) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2a.pdf}}};
	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*6) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2a.pdf}}};
	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*5) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2a.pdf}}};
	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*4) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2b.pdf}}};
	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*3) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2b.pdf}}};
	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*2) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2b.pdf}}};
	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*1) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2b.pdf}}};
	\node [visible on=<1->] at (0,\matrixtwobottom+\matrixspace*0) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2b.pdf}}};

	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*9) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3a.pdf}}};
	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*8) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3a.pdf}}};
	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*7) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3a.pdf}}};
	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*6) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3a.pdf}}};
	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*5) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3a.pdf}}};
	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*4) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3b.pdf}}};
	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*3) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3b.pdf}}};
	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*2) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3b.pdf}}};
	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*1) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3b.pdf}}};
	\node [visible on=<1->] at (0,\matrixthreebottom+\matrixspace*0) (l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3b.pdf}}};
	\node [visible on=<2->] at (2.6,1.3) (m3) {\pgftext{\includegraphics[height=28mm]{../images/colormat1.pdf}}};
	\node [visible on=<2->] at (2.6,4.3) (m2) {\pgftext{\includegraphics[height=28mm]{../images/colormat2.pdf}}};
	\node [visible on=<2->] at (2.6,7.3) (m1) {\pgftext{\includegraphics[height=28mm]{../images/colormat3.pdf}}};

    \node[visible on=<3->] at (8, 7.3) (s1) {$S_1$};
    \node[visible on=<3->] at (8, 4.3) (s2) {$S_2$};
    \node[visible on=<3->] at (8, 1.3) (s3) {$S_3$};

    \path[->] (5.2,7.3) edge [visible on=<3->,very thick, bend left] (s1);
    \path[->] (5.2,4.3) edge [visible on=<3->,very thick, bend left] (s2);
    \path[->] (5.2,1.3) edge [visible on=<3->,very thick, bend left] (s3);

\end{tikzpicture}
\end{center}
    % }
% \end{picture}
\end{frame}

\begin{frame}[t]
    % \frametitle{Easy as ABC}
    \begin{center}
    \begin{tikzpicture}[shorten >=1pt,node distance=2.2cm,on grid,auto]
        \node[] at (0,0) {\includegraphics<1>[width=\textwidth]{../images/rejection-sampling-observed.pdf}};
        \node[] at (0,0) {\includegraphics<2>[width=\textwidth]{../images/rejection-sampling-tolerance.pdf}};
        \node[] at (0,0) {\includegraphics<3>[width=\textwidth]{../images/rejection-sampling-10.pdf}};
        \node[] at (0,0) {\includegraphics<4>[width=\textwidth]{../images/rejection-sampling-100.pdf}};
        \node[] at (0,0) {\includegraphics<5>[width=\textwidth]{../images/rejection-sampling-200.pdf}};
        \node[] at (0,0) {\includegraphics<6>[width=\textwidth]{../images/rejection-sampling-500.pdf}};
        \node[] at (0,0) {\includegraphics<7>[width=\textwidth]{../images/rejection-sampling-1000.pdf}};
        \node[] at (0,0) {\includegraphics<8>[width=\textwidth]{../images/rejection-sampling-10000.pdf}};
        \node[] at (0,0) {\includegraphics<9>[width=\textwidth]{../images/rejection-sampling-20000.pdf}};
        \node[] at (0,0) {\includegraphics<10>[width=\textwidth]{../images/rejection-sampling-20000-post.pdf}};
        \node[visible on=<1->] at (-2.9, -3.7) (s1) {$S_1$};
        \node[visible on=<1->] at (3.4, -2.9) (s2) {$S_2$};
        \node[visible on=<1->] at (5.3, 0.7) (s3) {$S_3$};
    \end{tikzpicture}
    \end{center}
    % \centerline{
    % \includegraphics<1>[width=\textwidth]{../images/rejection-sampling-observed.pdf}
    % \includegraphics<2>[width=\textwidth]{../images/rejection-sampling-tolerance.pdf}
    % \includegraphics<3>[width=\textwidth]{../images/rejection-sampling-10.pdf}
    % \includegraphics<4>[width=\textwidth]{../images/rejection-sampling-100.pdf}
    % \includegraphics<5>[width=\textwidth]{../images/rejection-sampling-200.pdf}
    % \includegraphics<6>[width=\textwidth]{../images/rejection-sampling-500.pdf}
    % \includegraphics<7>[width=\textwidth]{../images/rejection-sampling-1000.pdf}
    % \includegraphics<8>[width=\textwidth]{../images/rejection-sampling-10000.pdf}
    % \includegraphics<9>[width=\textwidth]{../images/rejection-sampling-20000.pdf}
    % \includegraphics<10>[width=\textwidth]{../images/rejection-sampling-20000-post.pdf}
    % }
\end{frame}

>>>>

\tikzstyle{nAfill} = [fill=purple!25]
\tikzstyle{nCfill} = [fill=green!25]
\tikzstyle{nGfill} = [fill=orange!25]
\tikzstyle{nTfill} = [fill=blue!25]
\tikzstyle{nucA} = [draw=black, nAfill,
    minimum width=2.3ex, minimum height=2.3ex, node distance=2.3ex]
\tikzstyle{space} = [
    minimum width=2.3ex, minimum height=2.3ex, node distance=2.3ex]
\tikzstyle{lizard} = [
    minimum width=0ex, minimum height=0ex, node distance=0ex]
\tikzstyle{nucC} = [nucA, nCfill]
\tikzstyle{nucG} = [nucA, nGfill]
\tikzstyle{nucT} = [nucA, nTfill]

\begin{frame}[t]
    % \frametitle{Easy as ABC}
    \begin{columns}
        \column{0.2\textwidth}
        \includegraphics<1->[width=1.0\columnwidth]{../images/dmc-cartoon-islands-crop.pdf}
        \column{0.8\textwidth}
    \begin{center}
    \begin{tikzpicture}[font=\sffamily]

        \node[visible on=<2->, name=m1r01c01, nucA] {\nA};
        \node[visible on=<2->, name=m1r02c01, nucA, below of=m1r01c01] {\nA};
        \node[visible on=<2->, name=m1r03c01, nucA, below of=m1r02c01] {\nA};
        \node[visible on=<2->, name=m1r04c01, nucG, below of=m1r03c01] {\nG};
        \node[visible on=<2->, name=m1r05c01, nucG, below of=m1r04c01] {\nG};
        \node[visible on=<2->, name=m1r06c01, nucG, below of=m1r05c01] {\nG};

        \node[visible on=<2->, name=m1r01c02, nucC, right of=m1r01c01] {\nC};
        \node[visible on=<2->, name=m1r02c02, nucC, below of=m1r01c02] {\nC};
        \node[visible on=<2->, name=m1r03c02, nucC, below of=m1r02c02] {\nC};
        \node[visible on=<2->, name=m1r04c02, nucC, below of=m1r03c02] {\nC};
        \node[visible on=<2->, name=m1r05c02, nucC, below of=m1r04c02] {\nC};
        \node[visible on=<2->, name=m1r06c02, nucC, below of=m1r05c02] {\nC};

        \node[visible on=<2->, name=m1r01c03, nucG, right of=m1r01c02] {\nG};
        \node[visible on=<2->, name=m1r02c03, nucG, below of=m1r01c03] {\nG};
        \node[visible on=<2->, name=m1r03c03, nucG, below of=m1r02c03] {\nG};
        \node[visible on=<2->, name=m1r04c03, nucG, below of=m1r03c03] {\nG};
        \node[visible on=<2->, name=m1r05c03, nucG, below of=m1r04c03] {\nG};
        \node[visible on=<2->, name=m1r06c03, nucG, below of=m1r05c03] {\nG};

        \node[visible on=<2->, name=m1r01c04, nucA, right of=m1r01c03] {\nA};
        \node[visible on=<2->, name=m1r02c04, nucA, below of=m1r01c04] {\nA};
        \node[visible on=<2->, name=m1r03c04, nucA, below of=m1r02c04] {\nA};
        \node[visible on=<2->, name=m1r04c04, nucA, below of=m1r03c04] {\nA};
        \node[visible on=<2->, name=m1r05c04, nucA, below of=m1r04c04] {\nA};
        \node[visible on=<2->, name=m1r06c04, nucT, below of=m1r05c04] {\nT};

        \node[visible on=<2->, name=m1r01c05, nucA, right of=m1r01c04] {\nA};
        \node[visible on=<2->, name=m1r02c05, nucA, below of=m1r01c05] {\nA};
        \node[visible on=<2->, name=m1r03c05, nucA, below of=m1r02c05] {\nA};
        \node[visible on=<2->, name=m1r04c05, nucA, below of=m1r03c05] {\nA};
        \node[visible on=<2->, name=m1r05c05, nucA, below of=m1r04c05] {\nA};
        \node[visible on=<2->, name=m1r06c05, nucA, below of=m1r05c05] {\nA};

        \node[visible on=<2->, name=m1r01c06, nucT, right of=m1r01c05] {\nT};
        \node[visible on=<2->, name=m1r02c06, nucT, below of=m1r01c06] {\nT};
        \node[visible on=<2->, name=m1r03c06, nucC, below of=m1r02c06] {\nC};
        \node[visible on=<2->, name=m1r04c06, nucC, below of=m1r03c06] {\nC};
        \node[visible on=<2->, name=m1r05c06, nucC, below of=m1r04c06] {\nC};
        \node[visible on=<2->, name=m1r06c06, nucC, below of=m1r05c06] {\nC};

        \node[visible on=<2->, name=m1r01c07, nucG, right of=m1r01c06] {\nG};
        \node[visible on=<2->, name=m1r02c07, nucG, below of=m1r01c07] {\nG};
        \node[visible on=<2->, name=m1r03c07, nucG, below of=m1r02c07] {\nG};
        \node[visible on=<2->, name=m1r04c07, nucG, below of=m1r03c07] {\nG};
        \node[visible on=<2->, name=m1r05c07, nucG, below of=m1r04c07] {\nG};
        \node[visible on=<2->, name=m1r06c07, nucG, below of=m1r05c07] {\nG};

        \node[visible on=<2->, name=m1r01c08, nucT, right of=m1r01c07] {\nT};
        \node[visible on=<2->, name=m1r02c08, nucT, below of=m1r01c08] {\nT};
        \node[visible on=<2->, name=m1r03c08, nucT, below of=m1r02c08] {\nT};
        \node[visible on=<2->, name=m1r04c08, nucT, below of=m1r03c08] {\nT};
        \node[visible on=<2->, name=m1r05c08, nucT, below of=m1r04c08] {\nT};
        \node[visible on=<2->, name=m1r06c08, nucT, below of=m1r05c08] {\nT};

        \node[visible on=<2->, name=m1r01c09, nucG, right of=m1r01c08] {\nG};
        \node[visible on=<2->, name=m1r02c09, nucG, below of=m1r01c09] {\nG};
        \node[visible on=<2->, name=m1r03c09, nucG, below of=m1r02c09] {\nG};
        \node[visible on=<2->, name=m1r04c09, nucG, below of=m1r03c09] {\nG};
        \node[visible on=<2->, name=m1r05c09, nucG, below of=m1r04c09] {\nG};
        \node[visible on=<2->, name=m1r06c09, nucG, below of=m1r05c09] {\nG};

        \node[visible on=<2->, name=m1r01c10, nucC, right of=m1r01c09] {\nC};
        \node[visible on=<2->, name=m1r02c10, nucC, below of=m1r01c10] {\nC};
        \node[visible on=<2->, name=m1r03c10, nucC, below of=m1r02c10] {\nC};
        \node[visible on=<2->, name=m1r04c10, nucT, below of=m1r03c10] {\nT};
        \node[visible on=<2->, name=m1r05c10, nucT, below of=m1r04c10] {\nT};
        \node[visible on=<2->, name=m1r06c10, nucT, below of=m1r05c10] {\nT};

        \node[visible on=<2->, name=vspace1, space, below of=m1r06c01] {};

        \node[visible on=<2->, name=m2r01c01, nucT, below of=vspace1] {\nT};
        \node[visible on=<2->, name=m2r02c01, nucT, below of=m2r01c01] {\nT};
        \node[visible on=<2->, name=m2r03c01, nucT, below of=m2r02c01] {\nT};
        \node[visible on=<2->, name=m2r04c01, nucC, below of=m2r03c01] {\nC};
        \node[visible on=<2->, name=m2r05c01, nucC, below of=m2r04c01] {\nC};
        \node[visible on=<2->, name=m2r06c01, nucC, below of=m2r05c01] {\nC};

        \node[visible on=<2->, name=m2r01c02, nucC, right of=m2r01c01] {\nC};
        \node[visible on=<2->, name=m2r02c02, nucC, below of=m2r01c02] {\nC};
        \node[visible on=<2->, name=m2r03c02, nucC, below of=m2r02c02] {\nC};
        \node[visible on=<2->, name=m2r04c02, nucC, below of=m2r03c02] {\nC};
        \node[visible on=<2->, name=m2r05c02, nucC, below of=m2r04c02] {\nC};
        \node[visible on=<2->, name=m2r06c02, nucC, below of=m2r05c02] {\nC};

        \node[visible on=<2->, name=m2r01c03, nucG, right of=m2r01c02] {\nG};
        \node[visible on=<2->, name=m2r02c03, nucG, below of=m2r01c03] {\nG};
        \node[visible on=<2->, name=m2r03c03, nucG, below of=m2r02c03] {\nG};
        \node[visible on=<2->, name=m2r04c03, nucG, below of=m2r03c03] {\nG};
        \node[visible on=<2->, name=m2r05c03, nucG, below of=m2r04c03] {\nG};
        \node[visible on=<2->, name=m2r06c03, nucG, below of=m2r05c03] {\nG};

        \node[visible on=<2->, name=m2r01c04, nucC, right of=m2r01c03] {\nC};
        \node[visible on=<2->, name=m2r02c04, nucC, below of=m2r01c04] {\nC};
        \node[visible on=<2->, name=m2r03c04, nucT, below of=m2r02c04] {\nT};
        \node[visible on=<2->, name=m2r04c04, nucT, below of=m2r03c04] {\nT};
        \node[visible on=<2->, name=m2r05c04, nucT, below of=m2r04c04] {\nT};
        \node[visible on=<2->, name=m2r06c04, nucT, below of=m2r05c04] {\nT};

        \node[visible on=<2->, name=m2r01c05, nucA, right of=m2r01c04] {\nA};
        \node[visible on=<2->, name=m2r02c05, nucA, below of=m2r01c05] {\nA};
        \node[visible on=<2->, name=m2r03c05, nucA, below of=m2r02c05] {\nA};
        \node[visible on=<2->, name=m2r04c05, nucA, below of=m2r03c05] {\nA};
        \node[visible on=<2->, name=m2r05c05, nucA, below of=m2r04c05] {\nA};
        \node[visible on=<2->, name=m2r06c05, nucA, below of=m2r05c05] {\nA};

        \node[visible on=<2->, name=m2r01c06, nucC, right of=m2r01c05] {\nC};
        \node[visible on=<2->, name=m2r02c06, nucC, below of=m2r01c06] {\nC};
        \node[visible on=<2->, name=m2r03c06, nucC, below of=m2r02c06] {\nC};
        \node[visible on=<2->, name=m2r04c06, nucC, below of=m2r03c06] {\nC};
        \node[visible on=<2->, name=m2r05c06, nucC, below of=m2r04c06] {\nC};
        \node[visible on=<2->, name=m2r06c06, nucC, below of=m2r05c06] {\nC};

        \node[visible on=<2->, name=m2r01c07, nucG, right of=m2r01c06] {\nG};
        \node[visible on=<2->, name=m2r02c07, nucG, below of=m2r01c07] {\nG};
        \node[visible on=<2->, name=m2r03c07, nucG, below of=m2r02c07] {\nG};
        \node[visible on=<2->, name=m2r04c07, nucG, below of=m2r03c07] {\nG};
        \node[visible on=<2->, name=m2r05c07, nucG, below of=m2r04c07] {\nG};
        \node[visible on=<2->, name=m2r06c07, nucG, below of=m2r05c07] {\nG};

        \node[visible on=<2->, name=m2r01c08, nucT, right of=m2r01c07] {\nT};
        \node[visible on=<2->, name=m2r02c08, nucT, below of=m2r01c08] {\nT};
        \node[visible on=<2->, name=m2r03c08, nucT, below of=m2r02c08] {\nT};
        \node[visible on=<2->, name=m2r04c08, nucT, below of=m2r03c08] {\nT};
        \node[visible on=<2->, name=m2r05c08, nucT, below of=m2r04c08] {\nT};
        \node[visible on=<2->, name=m2r06c08, nucT, below of=m2r05c08] {\nT};

        \node[visible on=<2->, name=m2r01c09, nucA, right of=m2r01c08] {\nA};
        \node[visible on=<2->, name=m2r02c09, nucA, below of=m2r01c09] {\nA};
        \node[visible on=<2->, name=m2r03c09, nucA, below of=m2r02c09] {\nA};
        \node[visible on=<2->, name=m2r04c09, nucG, below of=m2r03c09] {\nG};
        \node[visible on=<2->, name=m2r05c09, nucG, below of=m2r04c09] {\nG};
        \node[visible on=<2->, name=m2r06c09, nucG, below of=m2r05c09] {\nG};

        \node[visible on=<2->, name=m2r01c10, nucC, right of=m2r01c09] {\nC};
        \node[visible on=<2->, name=m2r02c10, nucC, below of=m2r01c10] {\nC};
        \node[visible on=<2->, name=m2r03c10, nucC, below of=m2r02c10] {\nC};
        \node[visible on=<2->, name=m2r04c10, nucC, below of=m2r03c10] {\nC};
        \node[visible on=<2->, name=m2r05c10, nucC, below of=m2r04c10] {\nC};
        \node[visible on=<2->, name=m2r06c10, nucC, below of=m2r05c10] {\nC};

        \node[visible on=<2->, name=vspace2, space, below of=m2r06c01] {};

        \node[visible on=<2->, name=m3r01c01, nucC, below of=vspace2] {\nC};
        \node[visible on=<2->, name=m3r02c01, nucC, below of=m3r01c01] {\nC};
        \node[visible on=<2->, name=m3r03c01, nucC, below of=m3r02c01] {\nC};
        \node[visible on=<2->, name=m3r04c01, nucC, below of=m3r03c01] {\nC};
        \node[visible on=<2->, name=m3r05c01, nucC, below of=m3r04c01] {\nC};
        \node[visible on=<2->, name=m3r06c01, nucC, below of=m3r05c01] {\nC};

        \node[visible on=<2->, name=m3r01c02, nucA, right of=m3r01c01] {\nA};
        \node[visible on=<2->, name=m3r02c02, nucA, below of=m3r01c02] {\nA};
        \node[visible on=<2->, name=m3r03c02, nucA, below of=m3r02c02] {\nA};
        \node[visible on=<2->, name=m3r04c02, nucT, below of=m3r03c02] {\nT};
        \node[visible on=<2->, name=m3r05c02, nucT, below of=m3r04c02] {\nT};
        \node[visible on=<2->, name=m3r06c02, nucT, below of=m3r05c02] {\nT};

        \node[visible on=<2->, name=m3r01c03, nucG, right of=m3r01c02] {\nG};
        \node[visible on=<2->, name=m3r02c03, nucG, below of=m3r01c03] {\nG};
        \node[visible on=<2->, name=m3r03c03, nucG, below of=m3r02c03] {\nG};
        \node[visible on=<2->, name=m3r04c03, nucG, below of=m3r03c03] {\nG};
        \node[visible on=<2->, name=m3r05c03, nucG, below of=m3r04c03] {\nG};
        \node[visible on=<2->, name=m3r06c03, nucG, below of=m3r05c03] {\nG};

        \node[visible on=<2->, name=m3r01c04, nucT, right of=m3r01c03] {\nT};
        \node[visible on=<2->, name=m3r02c04, nucT, below of=m3r01c04] {\nT};
        \node[visible on=<2->, name=m3r03c04, nucT, below of=m3r02c04] {\nT};
        \node[visible on=<2->, name=m3r04c04, nucT, below of=m3r03c04] {\nT};
        \node[visible on=<2->, name=m3r05c04, nucC, below of=m3r04c04] {\nC};
        \node[visible on=<2->, name=m3r06c04, nucC, below of=m3r05c04] {\nC};

        \node[visible on=<2->, name=m3r01c05, nucA, right of=m3r01c04] {\nA};
        \node[visible on=<2->, name=m3r02c05, nucA, below of=m3r01c05] {\nA};
        \node[visible on=<2->, name=m3r03c05, nucA, below of=m3r02c05] {\nA};
        \node[visible on=<2->, name=m3r04c05, nucA, below of=m3r03c05] {\nA};
        \node[visible on=<2->, name=m3r05c05, nucA, below of=m3r04c05] {\nA};
        \node[visible on=<2->, name=m3r06c05, nucA, below of=m3r05c05] {\nA};

        \node[visible on=<2->, name=m3r01c06, nucC, right of=m3r01c05] {\nC};
        \node[visible on=<2->, name=m3r02c06, nucC, below of=m3r01c06] {\nC};
        \node[visible on=<2->, name=m3r03c06, nucC, below of=m3r02c06] {\nC};
        \node[visible on=<2->, name=m3r04c06, nucC, below of=m3r03c06] {\nC};
        \node[visible on=<2->, name=m3r05c06, nucC, below of=m3r04c06] {\nC};
        \node[visible on=<2->, name=m3r06c06, nucC, below of=m3r05c06] {\nC};

        \node[visible on=<2->, name=m3r01c07, nucC, right of=m3r01c06] {\nC};
        \node[visible on=<2->, name=m3r02c07, nucC, below of=m3r01c07] {\nC};
        \node[visible on=<2->, name=m3r03c07, nucC, below of=m3r02c07] {\nC};
        \node[visible on=<2->, name=m3r04c07, nucT, below of=m3r03c07] {\nT};
        \node[visible on=<2->, name=m3r05c07, nucT, below of=m3r04c07] {\nT};
        \node[visible on=<2->, name=m3r06c07, nucT, below of=m3r05c07] {\nT};

        \node[visible on=<2->, name=m3r01c08, nucG, right of=m3r01c07] {\nG};
        \node[visible on=<2->, name=m3r02c08, nucG, below of=m3r01c08] {\nG};
        \node[visible on=<2->, name=m3r03c08, nucG, below of=m3r02c08] {\nG};
        \node[visible on=<2->, name=m3r04c08, nucG, below of=m3r03c08] {\nG};
        \node[visible on=<2->, name=m3r05c08, nucG, below of=m3r04c08] {\nG};
        \node[visible on=<2->, name=m3r06c08, nucG, below of=m3r05c08] {\nG};

        \node[visible on=<2->, name=m3r01c09, nucG, right of=m3r01c08] {\nG};
        \node[visible on=<2->, name=m3r02c09, nucG, below of=m3r01c09] {\nG};
        \node[visible on=<2->, name=m3r03c09, nucG, below of=m3r02c09] {\nG};
        \node[visible on=<2->, name=m3r04c09, nucG, below of=m3r03c09] {\nG};
        \node[visible on=<2->, name=m3r05c09, nucG, below of=m3r04c09] {\nG};
        \node[visible on=<2->, name=m3r06c09, nucG, below of=m3r05c09] {\nG};

        \node[visible on=<2->, name=m3r01c10, nucT, right of=m3r01c09] {\nT};
        \node[visible on=<2->, name=m3r02c10, nucT, below of=m3r01c10] {\nT};
        \node[visible on=<2->, name=m3r03c10, nucT, below of=m3r02c10] {\nT};
        \node[visible on=<2->, name=m3r04c10, nucT, below of=m3r03c10] {\nT};
        \node[visible on=<2->, name=m3r05c10, nucT, below of=m3r04c10] {\nT};
        \node[visible on=<2->, name=m3r06c10, nucT, below of=m3r05c10] {\nT};

	    \node [visible on=<1->, left of=m1r01c01] (s1l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1a.pdf}}};
	    \node [visible on=<1->, left of=m1r02c01] (s1l2a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1a.pdf}}};
	    \node [visible on=<1->, left of=m1r03c01] (s1l3a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1a.pdf}}};
	    \node [visible on=<1->, left of=m1r04c01] (s1l1b) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1b.pdf}}};
	    \node [visible on=<1->, left of=m1r05c01] (s1l2b) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1b.pdf}}};
	    \node [visible on=<1->, left of=m1r06c01] (s1l3b) {\pgftext{\includegraphics[height=3mm]{../images/lizard-1b.pdf}}};

	    \node [visible on=<1->, left of=m2r01c01] (s2l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2a.pdf}}};
	    \node [visible on=<1->, left of=m2r02c01] (s2l2a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2a.pdf}}};
	    \node [visible on=<1->, left of=m2r03c01] (s2l3a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2a.pdf}}};
	    \node [visible on=<1->, left of=m2r04c01] (s2l1b) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2b.pdf}}};
	    \node [visible on=<1->, left of=m2r05c01] (s2l2b) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2b.pdf}}};
	    \node [visible on=<1->, left of=m2r06c01] (s2l3b) {\pgftext{\includegraphics[height=3mm]{../images/lizard-2b.pdf}}};

	    \node [visible on=<1->, left of=m3r01c01] (s3l1a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3a.pdf}}};
	    \node [visible on=<1->, left of=m3r02c01] (s3l2a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3a.pdf}}};
	    \node [visible on=<1->, left of=m3r03c01] (s3l3a) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3a.pdf}}};
	    \node [visible on=<1->, left of=m3r04c01] (s3l1b) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3b.pdf}}};
	    \node [visible on=<1->, left of=m3r05c01] (s3l2b) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3b.pdf}}};
	    \node [visible on=<1->, left of=m3r06c01] (s3l3b) {\pgftext{\includegraphics[height=3mm]{../images/lizard-3b.pdf}}};

        \node[visible on=<3->, name=m1hspace1, space, right of=m1r03c10] {};
        \node[visible on=<3->, name=m1hspace2, space, right of=m1hspace1] {};
        \node[visible on=<3->, name=m1hspace3, space, right of=m1hspace2] {};
        \node[visible on=<3->, name=m1hspace4, space, right of=m1hspace3] {};
        \node[visible on=<3->, name=m1hspace5, space, right of=m1hspace4] {};
        \node[visible on=<3->, name=s1, right of=m1hspace5, visible on=<1->] {$S_1$};

        \node[visible on=<3->, name=m2hspace1, space, right of=m2r03c10] {};
        \node[visible on=<3->, name=m2hspace2, space, right of=m2hspace1] {};
        \node[visible on=<3->, name=m2hspace3, space, right of=m2hspace2] {};
        \node[visible on=<3->, name=m2hspace4, space, right of=m2hspace3] {};
        \node[visible on=<3->, name=m2hspace5, space, right of=m2hspace4] {};
        \node[visible on=<3->, name=s2, right of=m2hspace5, visible on=<1->] {$S_2$};

        \node[visible on=<3->, name=m3hspace1, space, right of=m3r03c10] {};
        \node[visible on=<3->, name=m3hspace2, space, right of=m3hspace1] {};
        \node[visible on=<3->, name=m3hspace3, space, right of=m3hspace2] {};
        \node[visible on=<3->, name=m3hspace4, space, right of=m3hspace3] {};
        \node[visible on=<3->, name=m3hspace5, space, right of=m3hspace4] {};
        \node[visible on=<3->, name=s3, right of=m3hspace5, visible on=<1->] {$S_3$};

        \path[->] (m1hspace1) edge [visible on=<3->,very thick, bend left] (s1);
        \path[->] (m2hspace1) edge [visible on=<3->,very thick, bend left] (s2);
        \path[->] (m3hspace1) edge [visible on=<3->,very thick, bend left] (s3);
    \end{tikzpicture}
    \end{center}
    \end{columns}
\end{frame}

### 2015-03-05 slides/auburn/intro-mascot-tree.tex
Working on slides.

\begin{frame}
    \begin{center}
        % \transwipe<2>[direction=0, duration=3]
        % \includegraphics<2>[width=\textwidth]{../images/mascot-tree.png}
        \includegraphics[width=\textwidth]{../images/mascot-tree.png}

@@

>>>>

\begin{frame}
    \begin{center}
        % \transwipe<2>[direction=0, duration=3]
        % \includegraphics<2>[width=\textwidth]{../images/mascot-tree.png}
        \includegraphics<1>[width=\textwidth]{../mascot-tree/mascot-tree-shared.pdf}
        \includegraphics<2->[width=\textwidth]{../mascot-tree/mascot-tree-shared-events.pdf}

@@

\begin{frame}
    \begin{columns}
        \column{0.4\textwidth}
        \begin{minipage}[c]{\columnwidth}
        \begin{adjustwidth}{-2.3em}{}
        \begin{onlyenv}<1-6>
        \begin{itemize}
            \item<2-> Current phylogenetic methods assume events are independent 
            \item<3-> We know this assumption is frequently violated
            \item<4-> Why account for this non-independence?
            \begin{itemize}
                \item<5-> Improve phylogenetic inference
                \item<6-> Provide a general framework for inferring the affect
                    of community-scale processes of diversification
            \end{itemize}
        \end{itemize}
        \end{onlyenv}
        \end{adjustwidth}
        \end{minipage}

        \column{0.6\textwidth}
        \begin{minipage}[t][\textheight][c]{\linewidth}
        \centerline{
        \includegraphics<1->[width=\columnwidth]{../mascot-tree/mascot-tree-shared-events.pdf}
        }
        \end{minipage}
    \end{columns}
\end{frame}
